Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-05-30 second-draft/pnas-word-order-si.tex
SI

\textcolor{red}{TODO decide on formatting}

@@

	\begin{center}
\small{
\begin{tabular}{|c|c|ccc|c}
	\hline
	%&
& $\lambda = 0.0$
& $\lambda=1.0$\footnote{\url{https://aspredicted.org/blind.php?x=bg35x7}. Note that we report the locality results as `DLM' in Table~\ref{tab:all-predictions-1}, see also Section~\ref{sec:DLM}.} 
& $\lambda=0.9$\footnote{\url{http://aspredicted.org/blind.php?x=8gp2bt}}
& $\lambda=0.9$\footnote{\url{http://aspredicted.org/blind.php?x=ya4qf8}} 
	\\ \hline \hline 
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {1}}}}		  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_lifted_case.pdf}   }
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_case.pdf}     } 
 		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_case.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_case.pdf}     }  
		\\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {2}}}}	 
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_lifted_cop.pdf}   }
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_cop.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_cop.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_cop.pdf}     }  
		\\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}}}	 
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_aux.pdf}   }
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_aux.pdf}     }  reverse
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_aux.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_aux.pdf}     }  
		\\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {4}}}}	
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_nmod.pdf}   }
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_nmod.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_nmod.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_nmod.pdf}     }  
		\\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {5}}}}	 
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_acl.pdf}   }
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_acl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_acl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_acl.pdf}     }  
		\\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {6}}}}	
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_lifted_mark.pdf}   }
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_mark.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_mark.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_mark.pdf}     }  
		\\
&&&\\ \hline
	\multirow{2}{*}{	\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {7}}}}	
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_obl.pdf}   }
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_obl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_obl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_obl.pdf}     }  
		\\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {8}}}}	
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_perRelation_Parseability_xcomp.pdf}   }
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_xcomp.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_xcomp.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_xcomp.pdf}     }  
		\\
&&&\\ \hline
 \hline
\end{tabular}
}
	\end{center}
\caption{\textcolor{red}{parseability color, aux inversion}Results from previous optimization experiments with $\lambda=1.0$ (left) and $\lambda=0.9$ (center), and the main study (right).}\label{table:corr-resu}
\end{table}
	\begin{center}
\small{
\begin{tabular}{|c|ccc|c}
	\hline
	%&
& $\lambda=1.0$\footnote{\url{https://aspredicted.org/blind.php?x=bg35x7}. Note that we report the locality results as `DLM' in Table~\ref{tab:all-predictions-1}, see also Section~\ref{sec:DLM}.} 
& $\lambda=0.9$\footnote{\url{http://aspredicted.org/blind.php?x=8gp2bt}}
& $\lambda=0.9$\footnote{\url{http://aspredicted.org/blind.php?x=ya4qf8}} \\ \hline \hline 
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {1}}}}		  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_case.pdf}     } 
 		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_case.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_case.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {2}}}}	 
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_cop.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_cop.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_cop.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}}}	 
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_aux.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_aux.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_aux.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {4}}}}	
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_nmod.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_nmod.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_nmod.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {5}}}}	 
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_acl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_acl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_acl.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {6}}}}	
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_mark.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_mark.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_mark.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{	\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {7}}}}	
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_obl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_obl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_obl.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {8}}}}	
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_xcomp.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_xcomp.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_xcomp.pdf}     }  \\
&&&\\ \hline
 \hline
\end{tabular}
}
	\end{center}
\caption{Results from previous optimization experiments with $\lambda=1.0$ (left) and $\lambda=0.9$ (center), and the main study (right).}\label{table:corr-resu}
\end{table}

%\footnotetext{}
%  final experiment
%  0.9
%

\begin{figure}[ht]
	\begin{center}
	\includegraphics[width=0.25\textwidth]{../results/correlations/figures/posterior-satisfied-universals-together-large-prior-efficiency09.pdf}
	\includegraphics[width=0.25\textwidth]{../results/correlations/figures/posterior-satisfied-universals-together-large-prior-efficiency10.pdf}
	\end{center}
	\caption{(Other experiments) Posterior of the number of correlations correctly predicted by efficiency and its components, in a Bayesian multivariate mixed-effects logistic regression with random effects for languages and language families.}\label{fig:posterior-prior}
\end{figure}

>>>>

@@

	\begin{center}
\includegraphics[width=0.4\textwidth]{si-table-perrel-3-1.png}  
\end{center}

	\begin{center}
\begin{tabular}{cccc}
$\lambda=0.0$ & $\lambda=0.9$ & $\lambda=0.9$ & $\lambda=1.0$ \\
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-parseability.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-together-large-prior-efficiency09.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-efficiency-large.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-together-large-prior-efficiency10.pdf}
\end{tabular}
	\end{center}
\caption{Results from optimization experiments for different values of $\lambda$, including our two previous preregistered experiments. For comparison, we also show results for $\lambda=0$, corresponding to optimizing for parseability only (same results as reported in Tables (\ref{tab:all-predictions-1}-\ref{tab:all-predictions-2})). For $\lambda=0.9$, we report results from one preliminary preregistered experiment (left) and the final experiment (right). For $\lambda=1.0$, we report the other preliminary preregistered experiment.
Giving similar weight to parseability and predictability -- that is, $\lambda$ close to $1$ -- results in more accurate word order predictions than choosing a small value of $\lambda$ such as $\lambda=0.0$. Note that $\lambda$ cannot take values smaller than zero, or greater than one, see Section \ref{sec:lambda}.
}\label{table:corr-resu-previous}
\end{table}
